Mixed effect tweedie model in TMB

### 2019-03-15 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
Tweaks to temperature fitting script
Tweak fit temp

# FIXME: need to work out a bug in production on this new data set
# It's crashing TMB.
d_fit <- d_trawl
d_withheld <- d_trawl
spde <- make_spde(d_fit$X, d_fit$Y, n_knots = 200)
plot_spde(spde)

@@

# Try with a third degree polynomial:
m_temp3 <- sdmTMB(d_fit, temperature_c ~ 0 + as.factor(year) + poly(depth_scaled, 3),
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)

@@

predictions3_nd <- predict(m_temp3, newdata = sdmTMB::qcs_grid)

>>>>

# FIXME: need to work out a bug in production on this new data set
# It's crashing TMB.
d_fit <- d_trawl
d_withheld <- d_trawl
spde <- make_spde(d_fit$X, d_fit$Y, n_knots = 250)
plot_spde(spde)

@@

# Try with a third degree polynomial:
m_temp3 <- sdmTMB(d_fit, temperature_c ~ 0 + as.factor(year) + poly(depth_scaled, 3),
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = FALSE)

@@

predictions3_nd <- predict(m_temp3, newdata = sdmTMB::qcs_grid)
saveRDS(predictions3_nd$data, file = "analysis/tmb-sensor-explore/qcs-temp.rds")
